New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/weakschur.tex
theoreme schur et modification WS+

\subsection{Definition of \(WE_+\)}

\begin{definition}
Let \( n \in \mathbb{N}^*\), let\( b \in \mathbb{N}^*\) there exists a greatest integer that we note \(WE_b^+(n)\) such that \( [\![1, b+WE_b^+(n)]\!]\) can be partitionned into \(n\) weakly-sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
\\\\
\underline{\(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
\\\\
\underline{For \(A_n\) (the special subset):} \quad \(\forall (x,y) \in A_n^2,\)
\\
\[if \quad x+y>b+2WE_b^+(n),\quad x+y-2WE_b^+(n)\notin A_n\]
\\
\underline{For the others subsets:}\quad \(\forall (x,y) \in A_k^2\)
\\
\[
(Id+WE_b^+(n)\mathbf{1}_{ [\![0,b]\!]})(x+y[WE_b^+(n)]) \notin A_k
\]

\end{definition}

\begin{Theorem}
Let \( n \in \mathbb{N}^*\), let\( (a,b) \in (\mathbb{N}^*)^2\) such as \(a>b\). If there exist a partition of  
\end{Theorem}

>>>>

\subsection{Definition of \(WE_+\)}
\begin{definition}
Let \( (n,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, n]\!]\). This partition is said to be a (n,k,b)-weakly-sum-free template when:
\\\\
\underline{\(\forall i \in [\![1, k]\!], \quad A_i\) is weakly-sum-free}
\\\\
\underline{\(\forall i \in [\![1, k]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
\\\\
\underline{For \(A_k\) (the special subset):} \quad \(\forall (x,y) \in A_k^2,\)
\\
\[if \quad x+y>b+2(n-b),\quad x+y-2(n-b)\notin A_k\]
\\
\underline{For the others subsets:}\quad \(\forall i \in [\![0,k-1]\!], \forall(x,y) \in A_i^2\)
\\
\[
(Id+(n-b)\mathbf{1}_{ [\![0,b]\!]})(x+y[n-b]) \notin A_i
\]
\end{definition}
\\\\
\begin{definition}
Let \( (k,b) \in (\mathbb{N}^*)^2\), if there exist n such as there exist a partition of k subsets of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template, we note: 
\\\\\(WS_b^+=\max \{n\in \mathbb{N}^*\)/ there exists a partition of k-subsets of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template \}
\\\\
If this n does not exist, we set \(WS_b^+= 0\)
\end{definition}

\begin{definition}
Let \( n \in \mathbb{N}^*\), we define \(WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{WS_b^+(n)\}\) 
\end{definition}

\subsection{Lower bound for Weak schur numbers using Schur and Weak Schur template numbers}

\begin{theorem}
Let \((n,k,b) \in (\mathbb{N}*)^3\), let \( (m,p) \in (\mathbb{N}^*)^2\). If there exists a partition of p sum-free subsets of \([\![1,m]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template, then there exists a partition of (k+p-1) weakly sum-free subsets of \([\![1, b+c+m \times n]\!]\) with c=\(min A_n\bigcap [\![b+1, n]\!]\)-b-1
\end{theorem}
